Modelling with ANIMO:\\ between Fuzzy Logic and ODE

### 2015-04-27 Paper.tex
Added introduction to ANIMO, shortened conclusions

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={s.schivo@utwente.nl}   % email address
]{\inits{S}\fnm{Stefano} \snm{Schivo}}
\author[
   addressref={aff2},
   noteref={n1},
   email={j.scholma@utwente.nl}
]{\inits{J}\fnm{Jetse} \snm{Scholma}}
% \author[
%    addressref={aff3},
%    email={b.wanders@utwente.nl}
% ]{\inits{B}\fnm{Brend} \snm{Wanders}}
% \author[
%    addressref={aff2},
%    email={rauc6788@hotmail.com}
% ]{\inits{RA}\fnm{Ricardo A.} \snm{Urquidi Camacho}}
\author[
   addressref={aff3},
   email={p.e.vandervet@utwente.nl}
]{\inits{PE}\fnm{Paul E.} \snm{van~der~Vet}}
\author[
   addressref={aff2},
   email={h.b.j.karperien@utwente.nl}
]{\inits{M}\fnm{Marcel} \snm{Karperien}}
\author[
   addressref={aff2},
   %corref={aff2},
   email={j.n.post@utwente.nl}
]{\inits{JN}\fnm{Janine N.} \snm{Post}}
\author[
   addressref={aff1},
   %corref={aff1},
   email={j.c.vandepol@utwente.nl}
]{\inits{J}\fnm{Jaco} \snm{van~de~Pol}}
\author[
   addressref={aff1},
   corref={aff1},
   email={r.langerak@utwente.nl}
]{\inits{R}\fnm{Rom} \snm{Langerak}}

@@

\begin{abstract} % abstract <= 350 words. Headers: background, results, conclusions
\parttitle{Background}
The large amount of data which an experimental biologist
must deal with makes it nearly impossible to reason on
the dynamics of complex systems without relying on computational
support.
The software tool ANIMO (Analysis of Networks with Interactive MOdelling)
provides such computational support to the experimental biologist.
Models built with ANIMO allow to reason about the complex networks of signaling events
occurring in living cells.
The user-friendly interface allows biology experts to exploit formal methods
without the need to become experts also in mathematical formalisms.
\parttitle{Results}
ANIMO allows for a model precision that is intermediate between ordinary differential equations (ODEs)
and fuzzy logic.
We show this by presenting ANIMO models for two case studies: \emph{Drosophila melanogaster} circadian clock, and signal
transduction events downstream of TNF$\alpha$ and EGF in HT-29 human
colon carcinoma cells.
The models were originally developed with ODEs and
fuzzy logic respectively.
\parttitle{Conclusions}
% The software tool ANIMO, recently updated to work with the latest version of Cytoscape,
% allows the biologist to develop a formal model through a user friendly interface,
% achieving useful insight without the need to study any mathematical formalism.
%
ANIMO models allow to replicate with good precision the results of both the ODE and
fuzzy logic model. Moreover, ANIMO models require less parameters than ODEs and are more precise than
fuzzy logic: for this reason, we position the modelling paradigm of ANIMO
between ODEs and fuzzy logic.
\end{abstract}

@@

\section*{Background}\label{sec:introduction}
\subsection*{Modelling in cell biology}

Executable biology is a young subfield in computational modeling, aimed at constructing models that mimic
biological phenomena \emph{in silico}. It provides an interesting paradigm for enhancing network
diagrams with an underlying formal description of both network components and their interactions.
Executable models typically contain a description of the direct interactions of network components,
requiring the modeler to think in terms of
``cause and effect''. Biologists reason in similar ways about the molecular mechanisms of network
interactions, and this makes construction of an executable model an intuitive process.
ANIMO (Analysis of Networks with Interactive MOdeling,~\cite{animo-ieee,animo-gene})
provides an enabling technology to increase the use of computational models by experimental
 biologists without a thorough mathematical background. Such models are indispensable for formally
comparing experimental data to prior knowledge, or for structuring experimental findings into a
new theory.
When dealing with complex biological networks, executable biology models are particularly useful
to understand the non-linear dynamics and the entailed emergent properties of the networks.
In those cases, an ANIMO model can be used as a support to obtain insight based on abstract
representations of the interactions occurring inside living cells.
Other applications of ANIMO models include performing \emph{in silico} experiments and
the storage and transfer of knowledge on biological networks.

@@

\section*{Results}\label{sec:results}
\subsection*{Modelling oscillation}\label{sec:animo-drosophila}
Results obtained with ANIMO are comparable to results with other modeling
approaches. To demonstrate this, Figure~\ref{fig:drosophila-model}
represents an ANIMO model of the circadian clock in \emph{Drosophila Melanogaster}, based on~\cite{drosophila-ode-model},
where ordinary differential equations (ODEs) were used.
The cyclic behavior of the circadian clock is based on the alternating formation and destruction of the
CYC/CLK protein complex.
Concentration levels of this complex are in turn regulated by a series of proteins which are produced as
a consequence of CYC/CLK formation. The CWO protein
is central to the functioning of the network, as it degrades the mRNA for most of the involved proteins.
As such, CWO acts as an inhibitor that counterbalances the effect of CYC/CLK.
The positive influence of the light-regulated cryptochrome CRY on the degradation of TIM is a consequence
of the passage between day and night, allowing
the circadian clock to synchronize to a time zone (see Suppl. Sect.~\ref{suppl:repressilator}).

@@

\subsection*{Using ANIMO to generate hypotheses}\label{subsec:case-study-larger}
We constructed a model of the signaling network downstream of TNF$\alpha$ and EGF, formalizing
the crosstalk that takes place between the pathways at different levels of cellular regulation.
We first modeled the two pathways in isolation~(Suppl. Figs.~\ref{fig:large-model-tnf}, \ref{fig:large-model-egf}),
using information on protein interactions from
the KEGG~\cite{kegg} and phosphosite~\cite{phosphosite} databases. These models were fitted to experimental data
from previous studies~\cite{pathway-compendium,pathway-autocrine}.
We then merged the two pathways into a single model and added autocrine crosstalk between the pathways that has been
described in~\cite{pathway-autocrine}.
Briefly, stimulation with TNF$\alpha$ ({\sf TNFa} in the model) leads to a rapid release of TGF$\alpha$ ({\sf TGFa}),
which activates the EGF receptor ({\sf EGFR}).
This activation causes secretion of IL-1$\alpha$ ({\sf IL-1a}) at later time points.
The effect of IL-1$\alpha$ is down-regulated by the secretion of IL-1 receptor antagonist ({\sf IL-1ra})
downstream of TNF$\alpha$.
The resulting model (Fig.~\ref{fig:large-model-no-hypotheses}) was compared to the experimental data
for treatments with 100 ng/ml TNF alone and 100 ng/ml EGF alone (data not shown)~\cite{pathway-compendium}.

@@

@@

\subsection*{Future plans}
In order to enforce the concept of user interaction as a primary focus of the tool, we plan to extend
ANIMO by adding support for parameter sensitivity analysis and automatic parameter sweeps.
We already allow for only one numeric parameter per reaction, but an automatic way of adjusting such
parameters to fit experimental data will allow the user to concentrate more on defining a sensible topology for a pathway.
Such an automatic search could be limited by setting specific bounds on reaction rates based on previous knowledge,
or on a trade-off with performances.
Moreover, inspired by works on automata learning~\cite{test-based-modelling}, we plan to add also the possibility
to automatically derive a network topology based on experimental data and user-defined restrictions based on
previous knowledge.

We aim at widening the available set of model checking queries, in order to allow biologists to perform
in silico experiments on an already fitting model and to obtain answers to more relevant questions.
This would increase the usefulness of a model as a help to drive wet-lab investigation.
In order to allow for meaningful in silico experiments, we plan to purposefully introduce user-defined non-deterministic 
parts in our models, which would allow for drug dosage investigations through model checking.
This can be done e.g. through the definition of intervals for the values of some reaction kinetic constants,
adding considerable uncertainty in the timing of those reactions.
A model of this type could then be interrogated with queries like ``How much X, Y and Z do we need to provide,
and at which time points, in order to obtain targets A, B and C to be active?''.
More useful results can be achieved through proper application of the statistical model checking part of UPPAAL~\cite{uppaal-smc} to
an extended version of our model to include realistically significant stochastic behavior.
Finally, in order to further improve performances, the applicability a multi-core model checking approach based on the
works by Dalsgaard et al.~\cite{uppaal-multi-core1}
is under study.

@@

% \subsection*{Abstraction of biochemical reactions to a Timed Automata model}\label{subsec:timed-automata}
% \def\ta{TA}
% \def\tas{TA}
% A Timed Automaton (\ta) consists of states and transitions between these states (Figs.~\ref{subfig:erk}, \ref{subfig:mek}).
% Each automaton has local clocks associated to it that allow to control residence in its states, and transitions between states.
% Communication channels enable synchronization of transitions in different automata. The synchronization between two
% automata on channel $c$ requires one automaton to send a message: $c!$ while the other automaton performs the
% corresponding action: $c?$ to receive the message. A simplified \tas\ model of the activation of extracellular
% regulated kinase (ERK) by MAPK ERK kinase (MEK) illustrates these basic properties of \tas\
% (Fig.~\ref{fig:abstraction-mek-erk}). In this example, MEK activity is not regulated and ERK can exist in two states,
% inactive or active. In the network visualization, each molecular species (e.g. ERK) is depicted as a single node,
% colored according to its activity (Fig.~\ref{subfig:mek-erk}).
% 
% We define the relative activity level of a molecular species or reactant as the fraction of molecules in
% the complete population of that species that are in the active (e.g. phosphorylated) state.
% Reactants in an ANIMO model have a user-defined number of activity levels between 2 and 100, depending for example on the quality
% of experimental data.
% Coarse-grained models have a low number of activity levels and are less precise,
% whereas fine-grained models have a higher number of activity levels and behave more like continuous models (see Fig.~\ref{fig:levels}).
% 
% Variable reaction rates are accounted for by having variable time constraints to transitions, fast
% reactions being reflected by small time values. These values depend on the current activity of the reactants involved.
% Using basic kinetic rate laws, time constraints are pre-computed for all possible activity levels and stored in a pair of tables
% (see Sect.~\ref{subsec:kinetics}). Each rate law relies on a single parameter that is set manually. When the activity level
% of one of the input variables to a reaction changes, the tables are used to update the reaction rates for all reactions involving this reactant (see Fig.~\ref{fig:ta-diagram})
% % provides an overview of the steps taken by a Timed Automaton describing the example reaction between MEK and ERK.
\subsection*{Modeling interactions with Timed Automata}\label{subsec:timed-automata}
\def\ta{TA}
\def\tas{TA}

@@

\begin{figure*}[htbp]
 \begin{center}
  \includegraphics[width=0.9\textwidth]{images/modeling_methods_spectrum_animo}
 \end{center}
\caption{\csentence{The spectrum of modeling methods, with the addition of ANIMO.}
The precision of ANIMO models is halfway between fuzzy logic and ODE. In addition, ANIMO
allows for an easier modeling experience thanks to a user-friendly interface based on
the widely used network modeling software Cytoscape.}
\end{figure*}

>>>>

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   %corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={s.schivo@utwente.nl}   % email address
]{\inits{S}\fnm{Stefano}~\snm{Schivo}}
\author[
   addressref={aff2},
   noteref={n1},
   email={j.scholma@utwente.nl}
]{\inits{J}\fnm{Jetse}~\snm{Scholma}}
% \author[
%    addressref={aff3},
%    email={b.wanders@utwente.nl}
% ]{\inits{B}\fnm{Brend}~\snm{Wanders}}
% \author[
%    addressref={aff2},
%    email={rauc6788@hotmail.com}
% ]{\inits{RA}\fnm{Ricardo A.}~\snm{Urquidi Camacho}}
\author[
   addressref={aff3},
   email={p.e.vandervet@utwente.nl}
]{\inits{PE}\fnm{Paul E.}~\snm{van~der~Vet}}
\author[
   addressref={aff2},
   email={h.b.j.karperien@utwente.nl}
]{\inits{M}\fnm{Marcel}~\snm{Karperien}}
\author[
   addressref={aff2},
   %corref={aff2},
   email={j.n.post@utwente.nl}
]{\inits{JN}\fnm{Janine N.}~\snm{Post}}
\author[
   addressref={aff1},
   %corref={aff1},
   email={j.c.vandepol@utwente.nl}
]{\inits{J}\fnm{Jaco}~\snm{van~de~Pol}}
\author[
   addressref={aff1},
   corref={aff1},
   email={r.langerak@utwente.nl}
]{\inits{R}\fnm{Rom}~\snm{Langerak}}

@@

\begin{abstract} % abstract <= 350 words. Headers: background, results, conclusions
\parttitle{Background}
The large amount of data which an experimental biologist
must deal with makes it nearly impossible to reason on
the dynamics of complex systems without relying on computational
support.
The software tool ANIMO (Analysis of Networks with Interactive MOdelling)
provides such computational support and allows to reason about the complex networks of signaling events occurring in living cells.
The user-friendly interface allows biology experts to exploit formal methods
without the need to become experts also in mathematical formalisms.
\parttitle{Results}
ANIMO models show a degree of precision that is intermediate between ordinary differential equations (ODEs) and fuzzy logic.
We show this by presenting ANIMO models for two case studies: \emph{Drosophila melanogaster} circadian clock, and signal
transduction events downstream of TNF$\alpha$ and EGF in HT-29 human
colon carcinoma cells.
The models were originally developed with ODEs and
fuzzy logic respectively.
\parttitle{Conclusions}
% The software tool ANIMO, recently updated to work with the latest version of Cytoscape,
% allows the biologist to develop a formal model through a user friendly interface,
% achieving useful insight without the need to study any mathematical formalism.
%
ANIMO models allow to replicate with good precision the results of both the ODE and
fuzzy logic models. Moreover, ANIMO models require less parameters than ODEs and are more precise than
fuzzy logic: for this reason, we position the modelling paradigm of ANIMO
between ODEs and fuzzy logic.
\end{abstract}

@@

\section*{Background}\label{sec:introduction}
\subsection*{Modelling in cell biology}
Executable biology is a young subfield in computational modeling, aimed at constructing models that mimic
biological phenomena \emph{in silico}. It provides an interesting paradigm for enhancing network
diagrams with an underlying formal description of both network components and their interactions.
Executable models typically contain a description of the direct interactions of network components,
requiring the modeler to think in terms of
``cause and effect''. Biologists reason in similar ways about the molecular mechanisms of network
interactions, and this makes construction of an executable model an intuitive process.
ANIMO (Analysis of Networks with Interactive MOdeling,~\cite{animo-ieee,animo-gene})
provides an enabling technology to increase the use of computational models by experimental
 biologists without a thorough mathematical background. Such models are indispensable for formally
comparing experimental data to prior knowledge, or for structuring experimental findings into a
new theory.
When dealing with complex biological networks, executable biology models are particularly useful
to understand the non-linear dynamics and the entailed emergent properties of the networks.
In those cases, an ANIMO model can be used as a support to obtain insight based on abstract
representations of the interactions occurring inside living cells.
Other applications of ANIMO models include performing \emph{in silico} experiments and
the storage and transfer of knowledge on biological networks.

\subsection*{A brief introduction to ANIMO}
The user interface of ANIMO is displayed in Figure~\ref{fig:cytoscape}, where we present an example of biological network enriched with dynamic information. ANIMO is based on Cytoscape~\cite{cytoscape}, a software tool developed to represent biological networks. On top of the static topological information displayed in Cytoscape, ANIMO represents biological interactions starting from the basic concept of \emph{activity}: each biological entity in an ANIMO model is considered to be either active or inactive. Activity is to be intended in a very broad sense: for example, an active gene is being transcribed, an active kinase can perform phosphorylations, etc. Each node in an ANIMO network represents both active and inactive entities of the same type, with the relative amount of active entities represented by the node color on a user-configurable scale. Interactions among nodes define how the biological entities in a network influence each other's activity. Only nodes whose activity is larger than 0 can have an influence on their downstream targets, and only if that influence is not counterbalanced by intervening opposite interactions. For example, the interaction $A\rightarrow B$ indicates that node A, if active, will increase the activity of node B. If we add an additional interaction to the example, $C \dashv$\hspace{0.1em}$B$, with C also active, then the activity of B will change depending on the activity levels of A and C, and on the \emph{strength} of their influence. The strength of an ANIMO interaction is a scale factor $k$ which defines the speed at which that interaction occurs: higher values of $k$ give faster interactions. These $k$-values are the only parameters needed in an ANIMO model, and can be given in either a quantitative (as real numbers) or a qualitative way, choosing among self-explanatory descriptions such as ``very slow'', ``slow'', ``medium'', ``fast'', ``very fast''.

ANIMO models are analyzed to produce graphs showing how the activity of selected nodes change with time, allowing the user to obtain a view on the dynamic behavior of their network. In order to obtain these results, a model defined in ANIMO is automatically translated into its corresponding representation as a network of Timed Automata~\cite{timed-automata-alur-dill} and then analyzed \emph{behind the scenes} with the software tool UPPAAL~\cite{uppaal}. The formal language of Timed Automata allows to represent and analyze complex behaviors precisely and efficiently, but the user does not need to understand how Timed Automata or UPPAAL work, as the analysis process is made transparent. A fastidious user can still access the underlying models and perform other analyses in UPPAAL, but that is not required in order to fully profit from ANIMO.

A detailed description on how the Timed Automata models defined by ANIMO work, and how the results are obtained, can be found in~\cite{animo-ieee}. The choice of parameters for ANIMO models is described in~\cite{animo-syncop}. Additional guidance on the design of ANIMO models and how to best profit from biological experimental data can be found in~\cite{animo-gene}.

Figure~\ref{fig:animo-spectrum} shows the position of ANIMO into a spectrum of modeling methods: justification for this placement will be given in the Results section.

@@

\section*{Results}\label{sec:results}
\subsection*{Modelling oscillation}\label{sec:animo-drosophila}
Results obtained with ANIMO are comparable to results from widely used modeling
approaches. To demonstrate this, we present in Figure~\ref{fig:drosophila-model}
an ANIMO model of the circadian clock in \emph{Drosophila Melanogaster}, based on~\cite{drosophila-ode-model},
where ordinary differential equations (ODEs) were used.
The cyclic behavior of the circadian clock is based on the alternating formation and destruction of the
CYC/CLK protein complex.
Concentration levels of this complex are in turn regulated by a series of proteins which are produced as
a consequence of CYC/CLK formation. The CWO protein
is central to the functioning of the network, as it degrades the mRNA for most of the involved proteins.
As such, CWO acts as an inhibitor that counterbalances the effect of CYC/CLK.
The positive influence of the light-regulated cryptochrome CRY on the degradation of TIM is a consequence
of the passage between day and night, allowing
the circadian clock to synchronize to a time zone (see Suppl. Sect.~\ref{suppl:repressilator}).

@@

\subsection*{Using ANIMO to generate hypotheses}\label{subsec:case-study-larger}
We now present a comparison with an existing fuzzy logic model, which we use also as an example of how ANIMO can be used to create reference networks and help to reason on complex biological events.

We constructed a model of the signaling network downstream of TNF$\alpha$ and EGF, formalizing
the crosstalk that takes place between the pathways at different levels of cellular regulation.
We first modeled the two pathways in isolation~(Suppl. Figs.~\ref{fig:large-model-tnf}, \ref{fig:large-model-egf}),
using information on protein interactions from
the KEGG~\cite{kegg} and phosphosite~\cite{phosphosite} databases. These models were fitted to experimental data
from previous studies~\cite{pathway-compendium,pathway-autocrine}.
We then merged the two pathways into a single model and added autocrine crosstalk between the pathways that has been
described in~\cite{pathway-autocrine}.
Briefly, stimulation with TNF$\alpha$ ({\sf TNFa} in the model) leads to a rapid release of TGF$\alpha$ ({\sf TGFa}),
which activates the EGF receptor ({\sf EGFR}).
This activation causes secretion of IL-1$\alpha$ ({\sf IL-1a}) at later time points.
The effect of IL-1$\alpha$ is down-regulated by the secretion of IL-1 receptor antagonist ({\sf IL-1ra})
downstream of TNF$\alpha$.
The resulting model (Fig.~\ref{fig:large-model-no-hypotheses}) was compared to the experimental data
for treatments with 100 ng/ml TNF alone and 100 ng/ml EGF alone (data not shown)~\cite{pathway-compendium}.

@@

In this paper we discussed the placement of ANIMO among other modeling paradigms and tools, highlighting ANIMO's strong points. Our aim is not to promote the use of ANIMO in any modeling effort, but to show where it best shines.

@@

%\subsection*{Future plans}
%In order to enforce the concept of user interaction as a primary focus of the tool, we plan to extend
%ANIMO by adding support for parameter sensitivity analysis and automatic parameter sweeps.
%We already allow for only one numeric parameter per reaction, but an automatic way of adjusting such
%parameters to fit experimental data will allow the user to concentrate more on defining a sensible topology for a pathway.
%Such an automatic search could be limited by setting specific bounds on reaction rates based on previous knowledge,
%or on a trade-off with performances.
%Moreover, inspired by works on automata learning~\cite{test-based-modelling}, we plan to add also the possibility
%to automatically derive a network topology based on experimental data and user-defined restrictions based on
%previous knowledge.
%
%We aim at widening the available set of model checking queries, in order to allow biologists to perform
%in silico experiments on an already fitting model and to obtain answers to more relevant questions.
%This would increase the usefulness of a model as a help to drive wet-lab investigation.
%In order to allow for meaningful in silico experiments, we plan to purposefully introduce user-defined non-deterministic
%parts in our models, which would allow for drug dosage investigations through model checking.
%This can be done e.g. through the definition of intervals for the values of some reaction kinetic constants,
%adding considerable uncertainty in the timing of those reactions.
%A model of this type could then be interrogated with queries like ``How much X, Y and Z do we need to provide,
%and at which time points, in order to obtain targets A, B and C to be active?''.
%More useful results can be achieved through proper application of the statistical model checking part of UPPAAL~\cite{uppaal-smc} to
%an extended version of our model to include realistically significant stochastic behavior.
%Finally, in order to further improve performances, the applicability a multi-core model checking approach based on the
%works by Dalsgaard et al.~\cite{uppaal-multi-core1}
%is under study.

@@

% \subsection*{Abstraction of biochemical reactions to a Timed Automata model}\label{subsec:timed-automata}
% \def\ta{TA}
% \def\tas{TA}
% A Timed Automaton (\ta) consists of states and transitions between these states (Figs.~\ref{subfig:erk}, \ref{subfig:mek}).
% Each automaton has local clocks associated to it that allow to control residence in its states, and transitions between states.
% Communication channels enable synchronization of transitions in different automata. The synchronization between two
% automata on channel $c$ requires one automaton to send a message: $c!$ while the other automaton performs the
% corresponding action: $c?$ to receive the message. A simplified \tas\ model of the activation of extracellular
% regulated kinase (ERK) by MAPK ERK kinase (MEK) illustrates these basic properties of \tas\
% (Fig.~\ref{fig:abstraction-mek-erk}). In this example, MEK activity is not regulated and ERK can exist in two states,
% inactive or active. In the network visualization, each molecular species (e.g. ERK) is depicted as a single node,
% colored according to its activity (Fig.~\ref{subfig:mek-erk}).
%
% We define the relative activity level of a molecular species or reactant as the fraction of molecules in
% the complete population of that species that are in the active (e.g. phosphorylated) state.
% Reactants in an ANIMO model have a user-defined number of activity levels between 2 and 100, depending for example on the quality
% of experimental data.
% Coarse-grained models have a low number of activity levels and are less precise,
% whereas fine-grained models have a higher number of activity levels and behave more like continuous models (see Fig.~\ref{fig:levels}).
%
% Variable reaction rates are accounted for by having variable time constraints to transitions, fast
% reactions being reflected by small time values. These values depend on the current activity of the reactants involved.
% Using basic kinetic rate laws, time constraints are pre-computed for all possible activity levels and stored in a pair of tables
% (see Sect.~\ref{subsec:kinetics}). Each rate law relies on a single parameter that is set manually. When the activity level
% of one of the input variables to a reaction changes, the tables are used to update the reaction rates for all reactions involving this reactant (see Fig.~\ref{fig:ta-diagram})
% % provides an overview of the steps taken by a Timed Automaton describing the example reaction between MEK and ERK.
\subsection*{Modeling biological interactions with Timed Automata}\label{subsec:timed-automata}
\def\ta{TA}
\def\tas{TA}

@@

\begin{figure*}[htbp]
 \begin{center}
  \includegraphics[width=0.9\textwidth]{images/modeling_methods_spectrum_animo}
 \end{center}
\caption{\csentence{The spectrum of modeling methods, with the addition of ANIMO.}
The precision of ANIMO models is halfway between fuzzy logic and ODE. In addition, ANIMO
allows for an easier modeling experience thanks to a user-friendly interface based on
the widely used network modeling software Cytoscape.\label{fig:animo-spectrum}}
\end{figure*}
